---
title: "Tutorial reproducibility"
author: 
  - "Lars Vilhuber"
date: 1 September  2025
editor_options: 
  chunk_output_type: console
---

```{r config,include=FALSE}
library(readr)
library(here)
library(knitr)
library(dplyr)
library(ggplot2)
library(qualtRics)
library(lubridate)
library(qrcode)
library(kableExtra)
library(stringr)
library(tidylog)

# qualtRics secrets are read from the environment:
# - QUALTRICS_API_KEY
# - QUALTRICS_BASE_URL
# Let's check that they are there:

message(Sys.getenv("QUALTRICS_BASE_URL"))

# The repository name

message(Sys.getenv("GITHUB_REPOSITORY"))

# Process the repository name to generate the URL
# - split the two components
# - combine them into a URL with 'github.io' in the middle

GITHUB_REPOSITORY <- Sys.getenv("GITHUB_REPOSITORY")
GITHUB_REPOSITORY_PARTS <- strsplit(GITHUB_REPOSITORY, "/")[[1]]
REPOSITORY_URL <- paste0("https://github.com/", GITHUB_REPOSITORY)
WEBSITE_URL <- paste0("https://", GITHUB_REPOSITORY_PARTS[1], ".github.io/", GITHUB_REPOSITORY_PARTS[2])

# Qualtrics data for Day 1:
# you can find this with all_surveys() %>% arrange(creationDate) %>% head()

QUALTRICS_FULL_URL <- "https://cornell.yul1.qualtrics.com/jfe/form"
QUALTRICS_DAY1 <- "SV_bBqbJ9cSSJdOBw2"

# Public Qualtrics URL for day 2

QUALTRICS_DAY2 <- "SV_cNkhKL69K2Ob7o2"

# Time when this was posted (discard anything before that)

QUALTRICS_DAY1_STIME <- ymd_hms("2025-01-01 23:59:00")
QUALTRICS_DAY2_STIME <- ymd_hms("2025-01-01 21:59:00")
QUALTRICS_DAY2_ETIME <- ymd_hms("2026-06-30 23:59:00")

if (!dir.exists(here::here("data"))) {
  dir.create(here::here("data"))
}
```

::: {.panel-tabset}


## Follow along

```{r qrcode}
#| echo: false

code <- qr_code(WEBSITE_URL)
plot(code)

```


## Survey 1

Please fill out this survey on background and skills, to provide us with information on who you are. It will help us improve the presentation, and make it more relevant for you.

:::::: {.columns}
::: {.column}

<`r file.path(QUALTRICS_FULL_URL,QUALTRICS_DAY1)`>

:::
::: {.column}

```{r qrcode2}
#| echo: false

code2 <- qr_code(file.path(QUALTRICS_FULL_URL,QUALTRICS_DAY1))
plot(code2)

```


:::
::::::

## Slides

- [Intro](https://larsvilhuber.github.io/syracuse-seminar-2026-slides/)
- [Draft main part](https://labordynamicsinstitute.github.io/reproducibility-confidential-expanded/)

## Results 

*Last updated: `r format(Sys.time(), "%d %B %Y, %H:%M")`*

> The results cover multiple workshops, and include all responses between `r format(QUALTRICS_DAY1_STIME, "%d %B %Y")` and `r format(QUALTRICS_DAY2_ETIME, "%d %B %Y")`.

```{r downloaddata, child=c(here::here('pieces','01_downloaddata.Rmd'))}
```

```{r education, child=c(here::here('pieces','02_table_education.Rmd'))}
```

```{r os, child=c(here::here('pieces','02_table_os.Rmd'))}
```


```{r lang, child=c(here::here('pieces','02_table_lang.Rmd'))}
```

```{r cmdline, child=c(here::here('pieces','02_table_cmdline.Rmd'))}
```


## Additional

One of the following (or a linear combination):

- [Advanced self-checking of reproducibility](https://larsvilhuber.github.io/self-checking-reproducibility/presentation/)
- [Preserving raw survey data early in research lifecycle (ethically!)](https://labordynamicsinstitute.github.io/tutorial-preserving-survey/presentation/)




```{r, child=c(here::here('99-links.md'))}
```

:::

